Windowed Developer Topic Analysis

### 2009-04-04 lda-paper.tex
abstract

  During different periods, developers focus on different topics and
  different tasks during development. Stake-holders, such as managers,
  not directly involved with the development might have less awareness
  of the project and the topics and tasks that the developers are
  focussed on.  Imagine the scenario where a manager is trying to
  discover where all the developers' effort went after features have
  not been implemented because the developers unexpectedly had to deal
  with issues orthogonal to these features.  We propose to help
  stake-holder understand the topics of development by extracting
  topics from the descriptions of changes that programmers provide
  when they make changes.  We leverage topic analysis tools such as
  Latent Dirichlet Allocation (LDA) or Latent Semantic Indexing (LSI)
  to analyze periods, such as months, within a project's
  lifetime. Previous work applied LDA and LSI to
  to a project's entire lifetime.  These tools associate
  descriptions with independent topics extracted from these
  descriptions.  We propose a visualization of changing development
  topics over time that allows us to see the evolving stream of topics
  of development occurring over time. We also show that windowed topic
  analysis offers benefits compare to entire lifetime topic analysis
  because of the independence of topics between windows.

>>>>

%   During different periods, developers focus on different topics and
%   different tasks during development. Stake-holders, such as managers,
%   not directly involved with the development might have less awareness
%   of the project and the topics and tasks that the developers are
%   focussed on.  Imagine the scenario where a manager is trying to
%   discover where all the developers' effort went after features have
%   not been implemented because the developers unexpectedly had to deal
%   with issues orthogonal to these features.  We propose to help
%   stake-holder understand the topics of development by extracting
%   topics from the descriptions of changes that programmers provide
%   when they make changes.  We leverage topic analysis tools such as
%   Latent Dirichlet Allocation (LDA) or Latent Semantic Indexing (LSI)
%   to analyze periods, such as months, within a project's
%   lifetime. Previous work applied LDA and LSI to
%   to a project's entire lifetime.  These tools associate
%   descriptions with independent topics extracted from these
%   descriptions.  We propose a visualization of changing development
%   topics over time that allows us to see the evolving stream of topics
%   of development occurring over time. We also show that windowed topic
%   analysis offers benefits compare to entire lifetime topic analysis
%   because of the independence of topics between windows.

During different periods, developers focus on different topics and
different tasks during development. Stake-holders, such as managers, who are
not directly involved with the project's development might have less awareness of the
project and the topics and tasks that the developers have focussed on.
Imagine the scenario where a manager is trying to discover where all the
developers' effort went after features have not been implemented because the
developers unexpectedly had to deal with issues orthogonal to these
features.  We propose to help stakeholders understand the topics of
development by extracting topics from the descriptions of changes that
programmers provide when they make commits.  We leverage topic analysis
tools such as Latent Dirichlet Allocation (LDA) or Latent Semantic Indexing
(LSI) to analyze periods, such as months, within a project's lifetime,
whereas previous work applied LDA and LSI to to a project's entire lifetime.  These
tools associate descriptions with independent topics extracted from these
descriptions.  
We propose a visualization of changing development topics
over time that allows us to see the evolving stream of topics of development
occurring over time. We demonstrate that windowed topic analysis offers
benefits over entire lifetime topic analysis because of the
independence of topics between windows.
